SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-23 maintex.tex
Minor revisions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

@@

%{\bf COMMENT: I am not sure the trimmed regions could be so limited. If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.} 
%The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy. Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin. Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin. To account for this, we ``trim" the stacked profiles where a radius bin contains data for less than 50\% of the total set of galaxies. We represent the trimmed regions in our figures with dashed lines. In Figure \ref{fig:ssfr_prof}, galaxies below \logm\ $\le$ 10.0 have their innermost radii bin trimmed due to insufficient coverage.

@@

The mass ratio here is defined as, 
\begin{equation}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}) and \citet{Thorp:2019} ({\it Blue}).}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic). From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the inclination angle, sin($i$).

Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

@@

@@

The mass ratio here is defined as, 
\begin{equation}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We emphasize that the MaNGA target is not always the more massive component of the pair. We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair survey, and \citet{Thorp:2019} ({\it Blue}), a post-merger survey.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
